Classifying galaxy spectra at $0.5<z<1$: an unsupervised approach

### 2017-06-24 sections0.08/results0.08.tex
PB edits

\section{Results and Discussion}
\label{sec: result}

% Sahar: might have to move some of this text around

    In this section we show the results of the neural networks trained using the \citetalias{Kinney96} template spectra.
    Training with \citetalias{Kinney96} templates results in networks that have regions corresponding to galaxies of known morphological type. 
    The trained networks can then be used to categorize other galaxies.

    In order to find a sufficient size for the trained networks, we created maps with sizes ranging from $1\times2$ to $50\times50$.
    Varying the grid size of the maps helps us to monitor whether tighter grouping of galaxies is due to their similar properties or a lack of map space to separate them.
    Based on the size of the data and SOM results, we found the optimum grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
    For each grid we created different SOMs with different learning factors, neighbourhood distances, and number of iterations to find the optimum.

    We started our analysis by creating 1D SOMs. 
    First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time in the 1D case (Section~\ref{sec: 1D_somz}).
    We also applied the K-means clustering method (Section~\ref{sec: Kmeansvssom}) to both the template and sample galaxies and compared the results with the results of the 1D SOMs.
    For 2D networks (Section~\ref{sec: 2D}), we found the optimum size for the network to be $12\times12$ and created two types of SOM to show different applications of 2D SOMs.

    For each generated network, we compare the results with the \citetalias{Kinney96} categorization.
    We also use these networks to classify the \citetalias{Hossein12} galaxy sample, and compare this classification with that from the supervised networks in \citetalias{Hossein12}.

\subsection{One-dimensional self-organizing maps and K-means clustering: templates}

\begin{figure*}
\begin{subfigure}[b]{0.49\textwidth}
\centering
\includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/classified_group_in_4cluster_kinney.pdf}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.49\textwidth}
\centering \includegraphics[width=.99\textwidth, height= 7.5cm]{k_means_images/classified_group_in_4cluster_som.pdf}
\end{subfigure}
\caption{Clustering the \citetalias{Kinney96} template spectra using K-means clustering (left) and SOM (right). Note that both methods randomly assign the initial values for their analysis, therefore the cluster number is only used for distinguishing cluster membership.}
\label{fig: som_k_means_4}
\end{figure*}

        We performed K-means clustering on the \citetalias{Kinney96} template spectra using 4 clusters \textbf{and then assigned each of the 142 galaxies in the \citetalias{Hossein12}  sample to the cluster with the closest centroid.}
        %We measured distance between the centroid of each cluster and spectra of each galaxy to classify galaxies using K-means method.

       % For a direct comparison between clustered spectra and templates, the spectral angle distance provides more information on the overall shape of spectra than a minimum chi-square method, which considers spectra as unrelated points in a high dimensional space. 
        %Using the spectral angle distance, the spectra are treated as connected entities, which helps the shapes of the spectra to be recognized. 
        %In other words, the similarity of spectra are considered based on the general shape of the spectra rather than comparing each point.
        %(Although an SOM uses the Euclidean distance to find the differences, using the information of all the spectra, at the same time the SOM algorithm can recognize the overall shapes and treat the spectra as connected entities as well. 
        %Hence, there is no need to use the spectral angle distance in the SOM method.)
    Fig.~\ref{fig: som_k_means_4} shows the clustering of the template spectra in 4 groups using both K-means and SOMs.
        In the K-means method empty clusters are not allowed. 
        Hence a $K=12$ clustering would produce one-object clusters as in Fig.~\ref{fig: k96}.
        Both methods shown in Fig.~\ref{fig: som_k_means_4} separated the most starburst-like and quiescent galaxies in a similar manner.
        However, they show discrepancies for spectral types between the extreme cases.

    \subsection{One-Dimensional Self-Organizing Maps}
    \label{sec: 1D_somz}
        \subsubsection{Training the Networks}
        \label{sec: 1Dt}
            To start our clustering, we assumed that galaxies can be divided into only two general types, quiescent and starburst.
            This corresponds to a network with only two neurons.
            We increased the size of the map gradually until the 12 input samples divide into the 12 neurons.

@@

            We increased the size of the maps gradually until the galaxies are divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} in Appendix~\ref{app: high_Z_1d_soms} and Figure~\ref{fig: 1by22T}).
            Since there are more nodes in higher grid SOMs, the algorithm 
            pays more attention to small differences between groups.
            If the templates from \citetalias{Kinney96} had completely distinct spectral types, then a $1\times12$-sized SOM would be expected to show 12 different groups each containing a single template.
            However, in Fig.~\ref{fig: 1by12T}, we see that three of the neurons contain two templates and three of them are empty.
            It is evident that there was no template in the \citetalias{Kinney96} sample that can fill those empty neurons.
            In Fig.~\ref{fig: 1by12T}, from left to right, templates with types B and E, SB3 and SB4, and SB1 and SB2 are the ones grouped together. 
            The SB3 and SB4 grouping breaks when we increase the size of the network to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 templates, however, remain in the same neuron until the size of the map is increased to $1\times20$~(Fig.~\ref{fig: 1by20T}).
            The separation between templates B and E only happens when the size of the SOM exceeds $1\times22$~(Fig.~\ref{fig: 1by22T}).
            \begin{figure*}
                \begin{subfigure}[b]{\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_22.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{\textwidth}
                    \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_22.png}
                \end{subfigure}
                \caption[Results of training network in $1\times22$~grid]{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
                \label{fig: 1by22T}
            \end{figure*}

@@

        \subsubsection{Classifying the Galaxy Sample}
         \label{sec: 1Dv}
            After training the networks as discussed in Section~\ref{sec: 1Dt}, we used them to classify the spectra derived from the fitted SEDs of the 142-galaxy sample from \citetalias{Hossein12}.
            The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
            Eighty of the galaxies have spectral types similar to those of the quiescent galaxies and the spectral types of the rest are similar to the starburst galaxies.
            The lower left panel shows the median spectrum of the 80 galaxies that were classified as quiescent. 
            These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
            the spectra clearly show the 4000\AA~break, one of the signatures of quiescent galaxies.
            The H$\alpha$ emission in the spectrum could be from galaxies with similar spectral types to Sa galaxies, but with stronger emission lines.
            The median spectrum in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
            \begin{figure}
                \begin{subfigure}[b]{0.45\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.45\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by2_fluxdensity.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classification of fitted galaxy spectra from \citet{Hossein12} using the $1\times2$~network trained from the \citet{Kinney96} templates (Fig.~\ref{fig: 1by2T}). Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group. In this case 80 means that 80 of the 142 spectra are classified into the quiescent group while the 62 of the 142 spectra are categorized as starburst galaxies. Lower panel: median spectra of the galaxies in each group (flux densities are normalized by dividing spectra by flux density at 4000\AA), quiescent on the left and starburst on the right.}
                \label{fig: 1by2V}
            \end{figure}

            Since in this network galaxies were forced to be divided into a maximum of two groups, the strongest feature in a galaxy's spectrum predominantly decides to which group the galaxy belongs.
            Galaxies with a weak 4000\AA~break but strong emission lines and ultraviolet upturn are categorized as starbursts while galaxies with a strong 4000\AA~break are categorized as quiescent.
            Increasing the size of the SOM helps solve the problem of the galaxies which have features that are common in both groups.

@@

            In Fig.~\ref{fig: 1by22V}, we use the $1\times22$~network to classify the sample galaxies.
            As mentioned in Section~\ref{sec: 1Dt}, in this network size we observed the first separation of the \citetalias{Kinney96} galaxies into 12 different neurons.
            As in Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, the upper panel of Fig.~\ref{fig: 1by22V} shows the number of galaxies (out of the 142) belonging to each neuron in the $1\times22$ SOM.
            The lower panels present the median spectra of the galaxies in each neuron.
            Since galaxies had more space to separate, some of the neurons are left empty.
            Thus, instead of having 22 median spectra in the lower part of Fig.~\ref{fig: 1by22V}, there are only 14.

@@

            The first two neurons in the upper plot in Fig.~\ref{fig: 1by22V} are empty, while these neurons were occupied by galaxies B and E in the trained network.
            We therefore conclude that there are no galaxies in the \citetalias{Hossein12} sample with spectral type similar to that of type B or E.
            There are 3 galaxies in the third neuron, similar to the S0 type. 
            19 of the galaxies are in the fifth neuron and similar to the Sa type, while the 6 galaxies in the fourth neuron have spectral type similar to both S0 and Sa galaxies.
            There are 8 Sb type galaxies and 19 galaxies with spectral types similar to both Sa and Sb type galaxies.
            The following two neurons (eighth and ninth neurons from the left) are on the edge of the quiescent and starburst galaxies.
            In the upper panel in Fig.~\ref{fig: 1by22T}, the colour between these two neurons is black, which shows that these two are very different.
            Therefore, 24 galaxies in the eighth neuron have similar spectra to Sb type galaxies, and the spectra of the 5 galaxies in the ninth neuron are similar to the SB6 galaxies.
            The far right neurons in the network belong to galaxies with spectra comparable to types SB1 and SB2.

            In general, 56 galaxies correspond exactly to \citetalias{Kinney96} templates and the other 86 are placed between the initial 12 suggestions.
            As \citetalias{Hossein12} mentioned, part of the reason we could not classify all the galaxies using the \citetalias{Kinney96} model is that the model was constructed from co-adding spectra of 70 galaxies and have high uncertainties.
            Using this small sample, it is quite possible that the spectra from the best-fitting SEDs of 142 sample galaxies do not match any of the template ones perfectly.

           With other methods (e.g. $\chi^2$ fitting), trained neural network fitting of spectra is limited to models and the results are always reported with uncertainties.
            However, with SOM, we have the freedom to categorize galaxies into intermediate groups.
            Therefore, if the spectra of galaxies do not match completely with any of the  templates in Fig.~\ref{fig: k96}, they can be categorized as having a spectrum with similarity to two or more of the groups.

    \subsubsection{Properties of the Clustered Galaxies}

       In order to check whether our clustering in Sec.~\ref{sec: 1Dv}~is meaningful, in this section we examine the relations between median properties of the galaxies in each neuron.

@@

        Fig.~\ref{fig: props} shows the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in the $1\times2$, $1\times4$, and $1\times8$ networks.
        In all plots, the horizontal axis is the number of the neurons divided by the size of the network.
        As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from quiescent galaxies to starburst.
       Separating galaxies based on spectral types also leads to a separation in properties derived (via {\em CIGALE}) from the SEDs, as expected since the spectral types are also based on {\em CIGALE} fitting.

        {\em CIGALE} has various models to derive the properties of galaxies.
        Through these models, some of the properties are already known to be correlated with each other, e.g., stellar mass and star formation rate.
        \citetalias{Noll09} studied other relations between properties with no direct correlation in the models in a sample of SINGS galaxies.
        They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggests that younger stellar population correlates with higher SFR.
        They also found correlations between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
        Since in the {\em CIGALE} code, stellar mass is a free parameter, \citetalias{Noll09} argued that any stellar-mass-related correlation must be astrophysically meaningful. 
        They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
        \citetalias{Hossein12} replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than \citetalias{Noll09} results.

        \begin{figure*}
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f1.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f2.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f3.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f4.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f5.png}
        \end{subfigure}
       \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f6.png}
        \end{subfigure}
        \caption[Relations between properties of the clustered galaxies]{From top to bottom: Correlation between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass. Points show the median values of these properties of galaxies in $1\times22$ network and error bars are the standard deviation of the median values. Colours show the galaxy types in the new classification. The lightest grey (most pure red in the online version) colour shows E type galaxies and the black (most blue in the online version) one indicates the SB1 galaxies. The shading of other colours between light grey and black (red and blue in the online version) measures the location of galaxies along the SOM from  quiescent to starburst.}
        \label{fig: props_vs_props}
        \end{figure*}

        In order to compare our classifications with previous work, we produced similar plots to the ones in both \citetalias{Noll09} and \citetalias{Hossein12} (Fig.~\ref{fig: props_vs_props}).
        In Fig.~\ref{fig: props_vs_props}, the data points are median values of the properties of the galaxies in each neuron in Fig.~\ref{fig: 1by22V}, and error bars show the standard deviation of those properties.
        The colours show the galaxy types, where B type galaxies are shown with light grey (red in the online version) and SB1 types are shown with black (blue in the online version).
        The lighter grey (redder in the online version) the colour, the more similarity with quiescent galaxies, while the medium grey to black (purple to blue in the online version) colours show more similarity to starburst galaxies.
        Since in this method we allow galaxies to occupy classes in between the original \citetalias{Kinney96} templates, we have more than 12 colours in Fig.~\ref{fig: props_vs_props}.
        The medium grey (purple in the online version) point in the middle of the black (blue in the online version) points in Fig.~\ref{fig: props_vs_props} corresponds to galaxies with spectra similar to type Sc: the shape of their spectra indicates that they are old galaxies with high sSFR.

        The upper panels in Fig.~\ref{fig: props_vs_props} show the same relations as \citetalias{Noll09} and \citetalias{Hossein12}, but with more precision than those two, in all three plots.
        As mentioned in both \citetalias{Noll09} and \citetalias{Hossein12}, galaxies with smaller mass tend to be younger and more active.
        Fig.~\ref{fig: props} shows similar results: younger and more active galaxies have less stellar mass and more f$_{\rm {burst}}$.
        From older to younger galaxies, the colour of the points changes from light grey to black (red to blue in the online version), which shows a good correlation with their spectral type.

>>>>

\section{RESULTS AND DISCUSSION}
\label{sec: result}

    In this section we show the results of the neural networks and K-means clustering trained using the \citetalias{Kinney96} template spectra.
    Training with \citetalias{Kinney96} templates results in networks/clusters that have regions corresponding to galaxies of known morphological type. 
    The trained networks/clusters can then be used to categorize other galaxies.

    The first step in categorizing galaxies is choosing the number of classes.
    In the K-means method empty clusters are not allowed; 
    hence a $K=12$ clustering would produce one-object clusters as in Fig.~\ref{fig: k96}.
    We did not want to have too dense or too sparse clusters.
    Therefore we chose the number of clusters in the K-means clustering method to be $K=4$.
    Since empty neurons are allowed in SOMs, finding an optimal number of neurons for SOM networks is more subtle than just specifying a number of clusters. 
    In order to find a sufficient size for the trained neural networks, we created maps with sizes ranging from $1\times2$ to $50\times50$.
    Varying the grid size of the maps helps us to monitor whether tighter grouping of galaxies is due to their similar properties or a lack of map space to separate them.
    Based on the size of the data and SOM results, we found the optimum grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
    For each grid we created different SOMs with different learning factors, neighbourhood distances, and number of iterations to find the optimum.

    We started our analysis by creating 1D SOMs and K-means clustering. 
    First, we created SOMs with only two neurons ($1\times2$ map), and then increased the number of neurons one at a time (Section~\ref{sec: 1Dt}).
    We performed K-means clustering on the \citetalias{Kinney96} templates (Section~\ref{sec: Kmeansvssom}) and compared 
   the results with the results of the $1\times4$-sized 1D SOMs (Section~\ref{sec: Kmeansvssom}).
    For 2D networks (Section~\ref{sec: 2D}), we found the optimum size for the network to be $12\times12$ and created two types of SOM to show different applications of 2D SOMs.
    In Section~\ref{sec: Kmeansvssomvsann} we compare the results of the different classification in several ways. 
    For each generated neural network, we compare the results with the \citetalias{Kinney96} categorization.
    We also use these networks to classify the \citetalias{Hossein12} galaxy sample, and compare this classification with that from the supervised networks in \citetalias{Hossein12} and with K-means clustering.

    \subsection{One-dimensional self-organizing maps}
    \label{sec: 1D_somz}
        \subsubsection{Training the networks}
        \label{sec: 1Dt}
            To start our classification, we assumed that galaxies can be divided into only two general types, quiescent and starburst.
            This corresponds to a network with only two neurons.
            We increased the size of the map gradually until the 12 input samples divide into the 12 neurons.

@@

            We increased the size of the maps gradually until the templates were divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} in Appendix~\ref{app: high_Z_1d_soms} and Figure~\ref{fig: 1by22T}).
            Since there are more nodes in higher grid SOMs, the algorithm 
            pays more attention to small differences between groups.
            If the templates from \citetalias{Kinney96} had completely distinct spectral types, then a $1\times12$-sized SOM would be expected to show 12 different groups each containing a single template.
            However, in Fig.~\ref{fig: 1by12T}, we see that three of the neurons contain two templates and three of them are empty.
            It is evident that there was no template in the \citetalias{Kinney96} sample that can fill those empty neurons.
            In Fig.~\ref{fig: 1by12T}, from left to right, templates with types B and E, SB3 and SB4, and SB1 and SB2 are the ones grouped together. 
            The SB3 and SB4 grouping breaks when we increase the size of the network to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 templates, however, remain in the same neuron until the size of the map is increased to $1\times20$~(Fig.~\ref{fig: 1by20T}).
            The separation between templates B and E only happens when the size of the SOM exceeds $1\times22$~(Fig.~\ref{fig: 1by22T}).
            \begin{figure*}
                \begin{subfigure}[b]{\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/dist_1_by_22.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{\textwidth}
                    \includegraphics[width=\textwidth]{images0.01/1d/hit_t_1_by_22.png}
                \end{subfigure}
                \caption[Results of training network in $1\times22$~grid]{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
                \label{fig: 1by22T}
            \end{figure*}

@@

          \subsubsection{One-dimensional self-organizing maps and K-means clustering: templates}
          \label{sec: Kmeansvssom}

    \begin{figure*}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth, height=         7.5cm]{k_means_images/classified_group_in_4cluster_kinney.png}
    \end{subfigure}
    \hfill
        \begin{subfigure}[b]{0.49\textwidth}
        \centering \includegraphics[width=.99\textwidth, height=         7.5cm]{k_means_images/classified_group_in_4cluster_som.png}
    \end{subfigure}
    \caption{Clustering the \citetalias{Kinney96} template spectra using K-means clustering     (left) and SOM (right). Note that both methods randomly assign the initial values for their analysis, therefore the cluster number is only used for distinguishing cluster membership.}
    \label{fig: som_k_means_4}
    \end{figure*}

    We performed K-means clustering on the \citetalias{Kinney96} template spectra using 4 clusters.
    \textbf{
    Fig.~\ref{fig: som_k_means_4} shows the clustering of the template spectra into 4 groups using both K-means and SOMs.
    Both methods separated the most starburst-like and quiescent galaxies in a similar manner.
    However, they show discrepancies for spectral types between these extreme cases.
    Table~\ref{tab:kmeans_som4} shows the group assignments of the \citetalias{Kinney96} templates in the two methods.
    Templates B, E, S0 and Sa are grouped in the same cluster/neuron in both K-means and $1\times4$-sized SOM. 
    K-means grouped the Sb template with the above templates, but the SOM network classified it as a separate group.
    The K-means method clustered the Sc template as a separate group, while the SOM network grouped it with SB5 and SB6. 
    Another noticeable difference is that K-means clustered the SB1 and SB2 templates in one group and SB3 to SB6 in another while
    the SOM network grouped the SB1 to SB4 templates in one neuron and SB5 and SB6 in another.
    As Fig.~\ref{fig: som_k_means_4} shows, K-means clustering of the templates produced groups more similar to each other, while SOM emphasizes the templates' differences.
    }

    \begin{table}
    \centering
    \begin{tabular}{||l|c|c||}
    \hline
    \hline
    \citetalias{Kinney96} template & K-means group & SOM group \\
    \hline
    B                                & 3               & 1                         \\
    E                                & 3               & 1                         \\
    S0                               & 3               & 1                         \\
    Sa                               & 3               & 1                         \\
    Sb                               & 3               & 2                         \\
    Sc                               & 4               & 3                         \\
    SB1                              & 2               & 4                         \\
    SB2                              & 2               & 4                         \\
    SB3                              & 1               & 4                         \\
    SB4                              & 1               & 4                         \\
    SB5                              & 1               & 3                         \\
    SB6                              & 1               & 3                        \\
    \hline
    \end{tabular}
    \caption{Group assignments for \citetalias{Kinney96} template galaxies, using K-means and $1\times4$-sized SOM methods}
    \label{tab:kmeans_som4}
    \end{table}

        \subsubsection{Classifying the galaxy sample}
         \label{sec: 1Dv}

         \textbf{After training with the templates, we used both K-means and self-organizing maps to classify the 142 galaxies in the \citetalias{Hossein12} sample.
         K-means classification was performed by assigned each galaxy to the K-means cluster with the closest centroid and the results are discussed in Section~\ref{sec: Kmeansvssomvsann}.
        This section examines the results of one-dimensional SOM-based classification in detail.
         }

            The upper panel in Fig.~\ref{fig: 1by2V} shows the result of this classification using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
            Eighty of the galaxies have spectral types similar to those of the quiescent galaxies and the spectral types of the rest are similar to the starburst galaxies.
            The lower left panel shows the median spectrum of the 80 galaxies that were classified as quiescent. 
            These galaxies are similar to the ones in the left node in the upper panel of Fig.~\ref{fig: 1by2T}:
            the spectra clearly show the 4000\AA~break, one of the signatures of quiescent galaxies.
            The H$\alpha$ emission in the spectrum could be from galaxies with similar spectral types to Sa galaxies, but with stronger emission lines.
            The median spectrum in the lower right panel of Fig.~\ref{fig: 1by2V} shows strong emission lines and bright ultraviolet continuum, indications of a high star formation rate.
            \begin{figure}
                \begin{subfigure}[b]{0.45\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{images0.01/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.45\textwidth}
                     \includegraphics[width=\textwidth]{images0.01/1d/SED_total1by2_fluxdensity.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classification of fitted galaxy spectra from \citet{Hossein12} using the $1\times2$~network trained from the \citet{Kinney96} templates (Fig.~\ref{fig: 1by2T}). Upper panel: a hit map with the number in each node representing the number of galaxies belonging to that group. In this case 80 means that 80 of the 142 spectra are classified into the quiescent group while the 62 of the 142 spectra are categorized as starburst galaxies. Lower panel: median spectra of the galaxies in each group (flux densities are normalized by dividing spectra by flux density at 4000\AA), quiescent on the left and starburst on the right.}
                \label{fig: 1by2V}
            \end{figure}

            Since in this network galaxies were forced to be divided into a maximum of two groups, the strongest feature in a galaxy's spectrum predominantly decided to which group the galaxy belonged.
            Galaxies with a weak 4000\AA~break, strong emission lines and ultraviolet upturn are categorized as starbursts while galaxies with a strong 4000\AA~break are categorized as quiescent.
            Increasing the size of the SOM helps solve the problem of galaxies which have features that are common in both groups.

@@

            In Fig.~\ref{fig: 1by22V}, we use the $1\times22$~network to classify the sample galaxies.
            As mentioned in Section~\ref{sec: 1Dt}, in this network size we observed the first separation of the \citetalias{Kinney96} templates into 12 different neurons.
            As in Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, the upper panel of Fig.~\ref{fig: 1by22V} shows the number of galaxies (out of the 142) belonging to each neuron in the $1\times22$ SOM.
            The lower panels present the median spectra of the galaxies in each neuron.
            Since galaxies had more space to separate, some of the neurons are left empty.
            Thus, instead of having 22 median spectra in the lower part of Fig.~\ref{fig: 1by22V}, there are only 14.

@@

            The first two neurons in the upper plot in Fig.~\ref{fig: 1by22V} are empty, while these neurons were occupied by galaxies B and E in the trained network.
            We therefore conclude that there are no galaxies in the \citetalias{Hossein12} sample with spectral type similar to that of type B or E.
            There are 3 galaxies in the third neuron, similar to the S0 type. 
            19 of the galaxies are in the fifth neuron and similar to the Sa type, while the 6 galaxies in the fourth neuron have spectral type similar to both S0 and Sa galaxies.
            There are 8 Sb type galaxies and 19 galaxies with spectral types similar to both Sa and Sb.
            The following two neurons (eighth and ninth neurons from the left) are on the edge of the quiescent and starburst galaxies.
            In the upper panel in Fig.~\ref{fig: 1by22T}, the colour between these two neurons is black, which shows that these two are very different.
            Therefore, 24 galaxies in the eighth neuron have similar spectra to Sb type galaxies, and the spectra of the 5 galaxies in the ninth neuron are similar to the SB6 galaxies.
            The far right neurons in the network belong to galaxies with spectra comparable to types SB1 and SB2.

    \subsubsection{Properties of the spectral groups}

@@

       In order to check whether our clustering in Sec.~\ref{sec: 1Dv}~is meaningful, in this section we examine the relations between median properties of the galaxies in each group. 
          Fig.~\ref{fig: props} shows the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in the $1\times2$, $1\times4$, and $1\times8$ networks.
        In all plots, the horizontal axis is the number of the neurons divided by the size of the network.
        As shown in Fig.~\ref{fig: props}, in all three networks, stellar mass and age decrease while sSFR and $f_\mathrm{burst}$ increase as the type changes from quiescent galaxies to starburst.
       Separating galaxies based on spectral types also leads to a separation in properties derived (via {\em CIGALE}) from the SEDs, as expected since the spectral types are also based on {\em CIGALE} fitting.

        {\em CIGALE} has various models to derive the properties of galaxies.
        Through these models, some of the properties are already known to be correlated with each other, e.g., stellar mass and star formation rate.
        \citetalias{Noll09} studied other relations between properties with no direct correlation in the models in a sample of SINGS galaxies.
        They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggests that younger stellar population correlates with higher SFR.
        They also found correlations between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
        Since in the {\em CIGALE} code, stellar mass is a free parameter, \citetalias{Noll09} argued that any stellar-mass-related correlation must be astrophysically meaningful. 
        They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
        \citetalias{Hossein12} replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than in the \citetalias{Noll09} results.

        \begin{figure*}
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f1.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f2.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f3.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f4.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f5.png}
        \end{subfigure}
       \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{images0.01/1d/f6.png}
        \end{subfigure}
        \caption{From top to bottom: relations between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass. Square points show the median values of these properties of galaxies in the $1\times22$ SOM network and error bars are the standard deviation of the median values. Circles show the median value of properties inside each K-means cluster (using $K=4$) and asterisks show results from \citetalias{Hossein12}. Colours show the galaxy types in the SOM classification. The lightest grey (most pure red in the online version) colour shows E type galaxies and the black (most blue in the online version) indicates the SB1 galaxies. The shading of other colours between light grey and black (red and blue in the online version) measures the location of galaxies along the SOM from  quiescent to starburst.}
        \label{fig: props_vs_props}
        \end{figure*}

        In order to compare our classifications with previous work, we produced similar plots to the ones in both \citetalias{Noll09} and \citetalias{Hossein12} (Fig.~\ref{fig: props_vs_props}).
        In Fig.~\ref{fig: props_vs_props}, the point represent the median values of the properties of the galaxies in each group, with different symbol types representing classification method and error bars indicating the standard deviation of those properties.
       The colour scale represents neuron number in the SOM method, shading from quiescent to starburst. 
        Since in the $1\times22$-size SOM shown in Fig.~\ref{fig: 1by22V} we allow galaxies to occupy classes in between the original \citetalias{Kinney96} templates, there are more than 12 colours in Fig.~\ref{fig: props_vs_props}.
        The medium grey (purple in the online version) point in the middle of the black (blue in the online version) points in Fig.~\ref{fig: props_vs_props} corresponds to galaxies with spectra similar to type Sc: the shape of their spectra indicates that they are old galaxies with high sSFR.

        The upper panels in Fig.~\ref{fig: props_vs_props} show the same relations as \citetalias{Noll09} and \citetalias{Hossein12}, but with more precision than those two, in all three plots.
        % *** MORE PRECISION - NEED TO CLARIFY
        As mentioned in both \citetalias{Noll09} and \citetalias{Hossein12}, galaxies with smaller mass tend to be younger and more active.
        Fig.~\ref{fig: props} shows similar results: younger and more active galaxies have lower stellar mass and higher f$_{\rm {burst}}$.
        From older to younger galaxies, the colour of the points changes from light grey to black (red to blue in the online version), which shows a good correlation with their spectral type.

        \citetalias{Noll09} studied relations between A$_{\rm {FUV}}$ and other properties of galaxies and showed that the attenuation has no dependence on the specific star formation or age.
        In contrast to \citetalias{Noll09}, we find a correlation between A$_{\rm {FUV}}$ and these two parameters, shown in the lower panels of Fig.~\ref{fig: props_vs_props}.
        The general trend of the correlation between A$_{\rm {FUV}}$ and sSFR in Fig.~\ref{fig: props_vs_props} is similar to the trend found by \cite{Dale07}.
        They used IR luminosity to UV luminosity ratio (L$_{IR}$/L$_{FUV}$) as a measure of A$_{\rm {FUV}}$ and compared it with sSFR for all 75 galaxies in the SINGS survey.
        They found that for quiescent galaxies (E, S0 and S0/a), L$_{IR}$/L$_{FUV}$ (or A$_{\rm {FUV}}$) correlates with sSFR, and for spiral galaxies, there is an anticorrelation between L$_{IR}$/L$_{FUV}$ and sSFR.
        Since our sample has no E-type galaxies, we cannot confidently show the same correlation between A$_{\rm {FUV}}$ and sSFR. 
        However, it is clear in Fig.~\ref{fig: props_vs_props} that A$_{\rm {FUV}}$ increases with increasing sSFR in the S0 and Sa types.
        The correlation in the other types of galaxies is very similar to the one shown by \cite{Dale07}.
        Both \cite{Dale07} and \citetalias{Noll09} argued that these apparent trends can be a result of the dependence of star formation history on L$_{IR}$/L$_{FUV}$.
        Whether this dependence is real or not, our results here show that using self-organizing maps can separate spectra of galaxies in such a way that the characteristics of each of these groups are in agreement with the general picture of the galaxy evolution.
